Distance Sampling in \proglang{R}

### 2015-11-24 paper.Rmd
add Eric

---
author:
  - name: David L Miller
    affiliation: University of St Andrews
    address: >
      Centre for Research into Ecological and Environmental Modelling,
      The Observatory,
      St Andrews, Fife KY16 9LZ, Scotland
    email: dave@ninepointeightone.net
    url: http://converged.yt
  - name: Jeffrey L Laake
    affiliation: National Marine Mammal Laboratory
    address: >
      Alaska Fisheries Science Center
      7600 Sand Point Way N.E., Seattle, WA 98115, USA
    email: Jeff.Laake@noaa.gov
title:
  formatted: "Distance Sampling in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "Distance Sampling in R"
  # For running headers, if needed
  #short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [distance sampling, abundance estimation, line transects, point transects, "\\proglang{R}"]
  plain:     [distance sampling, abundance estimation, line transects, point transects, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{booktabs}
output: rticles::jss_article
bibliography: jstatsoft.bib
---

>>>>

---
author:
  - name: David L Miller
    affiliation: University of St Andrews
    address: >
      Centre for Research into Ecological and Environmental Modelling,
      The Observatory,
      St Andrews, Fife KY16 9LZ, Scotland
    email: dave@ninepointeightone.net
    url: http://converged.yt
  - name: Eric A Rexstad
    affiliation: University of St Andrews
    address: >
      Centre for Research into Ecological and Environmental Modelling,
      The Observatory,
      St Andrews, Fife KY16 9LZ, Scotland
    email: Eric.Rexstad@st-andrews.ac.uk
  - name: Jeffrey L Laake
    affiliation: National Marine Mammal Laboratory
    address: >
      Alaska Fisheries Science Center
      7600 Sand Point Way N.E., Seattle, WA 98115, USA
    email: Jeff.Laake@noaa.gov
title:
  formatted: "Distance Sampling in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "Distance Sampling in R"
  # For running headers, if needed
  #short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [distance sampling, abundance estimation, line transects, point transects, "\\proglang{R}"]
  plain:     [distance sampling, abundance estimation, line transects, point transects, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{booktabs}
output: rticles::jss_article
bibliography: jstatsoft.bib
---
